Paper_analyses

### 2021-09-04 Paper_Analyses_subj_obje_arousal.Rmd
First patch plot
made the plots and patchwork for the first big panel including a power point with some additional edits

 db_full4new_stim_screen_pupil_nopract %>%
   subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  # subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, color = mediansplit_sample_valence2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means()
  facet_grid(~mediansplit_sample_arousal2)

>>>>

# unique(db_full4new_stim_screen_pupil_nopract$ssid)
plots_paper$pupil_correlation <- db_full4new_stim_screen_pupil_nopract %>%
   subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  # subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, color = mediansplit_sample_valence2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = 0, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means()
  # facet_grid(~mediansplit_sample_arousal2)

  plots_paper$pupil_correlation+ p$graphstyle
```
